Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-12-15 ms.tex
fringing investigation from CV3 spectrum.

>>>>

The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec}, probably because of the broad PSF.
However, the CV3 image in Figure \ref{fig:cv3ExtractedSpectrum} shows a lot of structure in the spectrum.
\textcolor{red}{\bf Is this fringing?}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{fringing_placeholder.png}
\caption{The CV3 extracted spectrum shows dramatic structure.
Is this fringing?}\label{fig:cv3ExtractedSpectrum}
\end{figure}
